Magnetized Polish doughnuts revisited

### 2017-03-14 paper.tex
Minor correction to adjust the order of the figures
Add files via upload

\newcommand{\tf}[1]{\textcolor{red}{TF: #1}}

@@

   \author{Sergio Gimeno\inst{1}   \and Jos\'e A.~Font\inst{1,2} }

@@

   \keywords{\tf{Complete keywords}}

@@

Equilibrium tori around Kerr black holes are built assuming that the spacetime gravitational potentials and the fluid fields are stationary and axisymmetric. In all the derivations presented below, the Kerr metric is implicitely written using standard Boyer-Lindquist coordinates. It is convenient to introduce a number of relevant characteristic radii, such as the radius
of the marginally stable circular orbit, $r_{\rm ms}$, and the radius of the marginally bound circular orbit, $r_{\rm mb}$, given by
\begin{eqnarray}
r_{\rm ms} &=& M\,\left(3+Z_2-\left[(3-Z_1)(3+Z_1+2Z_2)\right]^{1/2})\right)\,,
\\
r_{\rm mb} &=& 2M\,\left(  1-\frac{a_*}{2} + \sqrt{1-a_*} \right)\,,
\end{eqnarray}
where we have defined the following quantities, $Z_1=1+(1-a_*^2)^{1/3}[(1+a_*)^{1/3}+(1-a_*)^{1/3}]$, $Z_2=(3a_*^2+Z_1^2)^{1/2}$, and $a_*=a/M$, with $a$ and $M$ being the spin Kerr parameter and the black hole mass. \tf{Check that the above expressions are correct.}

@@

\cite{Jaroszynski:1980} argued that the slope of the specific angular momentum should range between two cases, $l = \mathrm{const.}$ and $\Omega = \mathrm{const}$. Following \citet{Qian:2009} we assume an angular momentum distribution ansatz given by  
\begin{equation}
l (r,\theta) = \left\{ \label{eq:ansatz} 
  \begin{array}{lr}
    l_0 \left(\frac{l_{\mathrm{K}}(r)}{l_0}\right)^{\beta}\sin^{2\gamma}{\theta} &  \text{for } r \geq r_{\mathrm{ms}}\\
    l_{\mathrm{ms}}(r)\sin^{2\gamma}{\theta} & \text{for } r < r_{\mathrm{ms}}
  \end{array}
\right.
\end{equation}
where constants $l_0$ and $l_{\mathrm{ms}}(r)$ are defined by $l_0 \equiv \eta l_{\mathrm{K}}(r_{\mathrm{ms}})$ and $l_{\mathrm{ms}}(r) \equiv l_0 [l_{\mathrm{K}}(r_{\mathrm{ms}})/l_0]^{\beta}$. Therefore, the model for the distribution of angular momentum has three parameters $(\beta, \gamma, \eta)$, whose range of variation is given by~\citep{Qian:2009}
\begin{equation}
0 \leq \beta \leq 1, \quad -1 \leq \gamma \leq 1, \quad 1 \leq \eta \leq \eta_{\mathrm{max}},
\end{equation}
with $\eta_{\mathrm{max}} = l_{\mathrm{K}}(r_{\mathrm{mb}})/l_{\mathrm{K}}(r_{\mathrm{ms}})$. In this paper, and as it is done in~\citet{Qian:2009}, we choose $\eta = \eta_{\mathrm{max}}$, and then we can write $l_0$ as $l_0 = l_{\mathrm{K}}(r_{\mathrm{mb}})$. We take this choice because [explicar que esta eleccion hace que el momento angular esté comprendido entre lmb y lms para variaciones de beta entre 0 y 1. Además los discos de momento angular constante que empiezan en el cusp, no tienen borde externo para l = lmb] \tf{Write the explanation in the draft.}

@@

The equations of ideal general relativistic MHD are the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and 
$\nabla_{\mu} (\rho u^{\mu}) = 0$, 
%\begin{equation}\label{eq:e-m_cons}
%\nabla_{\mu} T^{\mu\nu} = 0,
%\end{equation}
%\begin{equation}\label{eq:cons_faraday}
%\nabla_{\mu} \ast F^{\mu\nu} = 0,
%\end{equation}
%\begin{equation}\label{eq:continuity}
%\nabla_{\mu} (\rho u^{\mu}) = 0,
%\end{equation}
where $\nabla_{\mu}$ is the covariant derivative and
\begin{equation}\label{eq:e-m_tensor}
T^{\mu\nu} = (w + b^2)u^{\mu}u^{\nu} + \left(p + \frac{1}{2}b^2\right)g^{\mu\nu} - b^{\mu}b^{\nu},
\end{equation}
is the energy-momentum tensor of a magnetized perfect fluid, $w$ and $p$ being the fluid enthalpy and pressure, respectively. 
Moreover,
%\begin{equation}
$^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$
%\end{equation}
is the (dual of the) Faraday tensor relative to an observer with four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame, with
$b^2=b^{\mu}b_{\mu}$. Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
and taking into account that the flow is stationary and axisymmetric, the conservation of the current density and of the Faraday tensor follow. Contracting Eq.~\eqref{eq:e-m_tensor} with the projection tensor $h^{\alpha}_{\beta} = \delta^{\alpha}_{\beta} + u^{\alpha}u_{\beta}$, we arrive at
\begin{equation}
(w + b^2)u_{\nu}\partial_i u^{\nu} + \partial_i\left(p + \frac{b^2}{2}\right) - b_{\nu}\partial_i b^{\nu}=0\,,
\end{equation}
where $i = r, \theta$. Following~\cite{Komissarov:2006} we rewrite this equation in terms of the specific angular momentum $l$ and the angular velocity $\Omega$, to obtain
\begin{equation}\label{eq:diff_ver}
\partial_i(\ln u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{w} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}w} = 0\,,
\end{equation}
where $\mathcal{L} = g_{t\phi}^2 - g_{tt}g_{\phi\phi}$.
To integrate Eq.~\eqref{eq:diff_ver} we first assume a barotropic equation of state $w = w(p)$ of the form
\begin{equation}\label{eq:eos_fluid}
p = K w^{\kappa},
\end{equation}
with $K$ and $\kappa$ constants.
Then, we define the magnetic pressure as $p_{\mathrm{m}} = b^2/2$, and introduce the definitions $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$ and $\tilde{w} = \mathcal{L} w$, in order to write an analog equation to Eq.~\eqref{eq:eos_fluid} for $\tilde{p}_{\mathrm{m}}$~\citep{Komissarov:2006}
\begin{equation}\label{eq:eos_mag_tilde}
\tilde{p}_{\mathrm{m}} = K_{\mathrm{m}} \tilde{w}_{\mathrm{m}}^{\eta},
\end{equation}
or, in terms of the magnetic pressure $p_{\mathrm{m}}$
\begin{equation}\label{eq:eos_mag}
p_{\mathrm{m}} = K_{\mathrm{m}} \mathcal{L}^{\eta-1} w^{\eta},
\end{equation}
where $K_{\mathrm{m}}$ and $\eta$ are constants. \tf{I think we should use a different letter for the exponent instead of $\eta$ as it can be confused with the $\eta$ in the angular momentum ansatz.}
This particular choice of relationships, $w = w(p)$ and $\tilde{w} = \tilde{w}(\tilde{p}_{\mathrm{m}})$, fulfill the general relativistic version of the von Zeipel theorem for a toroidal magnetic field~\citep{vonZeipel:1924, Zanotti:2015}, i.e.~the surfaces of constant $\Omega$ and constant $l$ coincide.

Integrating Eq.~\eqref{eq:diff_ver} we obtain
\begin{equation}\label{eq:pre_full_int}
\ln |u_t| - \int^l_0 \frac{\Omega \mathrm{d}l}{1 - \Omega l} + \int^p_0 \frac{\mathrm{d}p}{w} + \int_0^{\tilde{p}_{\mathrm{m}}} \frac{\mathrm{d}\tilde{p}_{\mathrm{m}}}{\tilde{w}} = \mathrm{const}.
\end{equation}
On the surface of the disk, and particularly on its inner edge, the conditions
$p = \tilde{p}_{\mathrm{m}} = 0, \; u_t = u_{t, \mathrm{in}}, \; l = l_{\mathrm{in}}$
are satisfied and, therefore, the integration constant is simply given by
\begin{equation}
\mathrm{const.} = \ln |u_t| - \int^l_{l_\mathrm{in}} \frac{\Omega \mathrm{d}l}{1 - \Omega l}\,.
\end{equation}
We can also introduce the total (gravitational plus centrifugal) potential $W$~\citep{Abramowicz:1978} and write the integral form of the equation of motion as
\begin{equation}\label{eq:potential}
W - W_{\mathrm{in}} = \ln|u_t| - \ln|u_{t,\mathrm{in}}| - \int^{l}_{l_{\mathrm{in}}} \frac{\Omega \mathrm{d}l}{1 - \Omega l},
\end{equation}
where $W_{\mathrm{in}}$ is the potential at the inner edge of the disk (in the equatorial plane). With this definition, we can write Eq.~\eqref{eq:pre_full_int} as
\begin{equation}\label{eq:full_int}
W - W_{\mathrm{in}} = \int^p_0 \frac{\mathrm{d}p}{w} + \int_0^{\tilde{p}_{\mathrm{m}}} \frac{\mathrm{d}\tilde{p}_{\mathrm{m}}}{\tilde{w}},
\end{equation}
which for a barotropic equation of state can be easily integrated to give
\begin{equation}\label{eq:pre_enthalpy_eq}
W - W_{\rm{in}} + \frac{\kappa}{\kappa - 1}\frac{p}{w} + \frac{\eta}{\eta - 1}\frac{p_{\mathrm{m}}}{w} = 0\,.
\end{equation}
Replacing $p$ and $p_{\mathrm{m}}$ by equations \eqref{eq:eos_fluid} and \eqref{eq:eos_mag}, the previous equation reduces to
\begin{equation}\label{eq:enthalpy_eq}
W - W_{\rm{in}} + \frac{\kappa}{\kappa - 1} K w^{\kappa - 1} + \frac{\eta}{\eta - 1}K_{\mathrm{m}}(\mathcal{L} w)^{\eta - 1} = 0,
\end{equation}
which relates the distribution of the potential with the distribution of enthalpy.

@@

\begin{figure*}[t]
\centering
\includegraphics[scale=0.16]{figures/fig1a.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.16]{figures/fig1b.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.16]{figures/fig1c.pdf}
\caption{Comparison with Komissarov's solution for a constant angular momentum model. The left panel shows the density distribution in logarithm scale for all radii and all angles while the middle and right panels show, respectively, the angular profile of the logarithm of the density at the centre of the disk and the radial profile of the density at the equatorial plane.}
           \label{komissarov}%
 \end{figure*}

@@

Next, we choose all the initial values for the integration of the equation \eqref{eq:F} to be between $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$ ($\theta = \pi / 2$). Since we are only interested in the surfaces inside the Roche lobe, our choice of initial values provides us a mapping of the equipotential surfaces of the torus. Given that we have already obtained both the equipotential surfaces which cross the segment $[r_{\mathrm{cusp}}, r_{\mathrm{c}}]$ and the potential distribution there, we found the potential distribution for the torus.
Once we have the potential distribution, we can find the gas pressure at the center, from equation \eqref{eq:enthalpy_eq}
\begin{equation}
p_{\mathrm{c}} = w_{\mathrm{c}}(W_{\mathrm{in}} - W_{\mathrm{c}})\left(\frac{\kappa}{\kappa - 1} + \frac{\eta}{\eta - 1}\frac{1}{\beta_{\mathrm{c}}}\right)^{-1},
\end{equation}
where $w_{\mathrm{m}}$ is the enthalpy at the disk center and
\begin{equation}
\label{eq:beta_eq}
\beta_{\mathrm{c}} = p/p_{\mathrm{m}},
\end{equation}
is the magnetization parameter (being $\beta_{\mathrm{m}}$ the magnetization parameter at the disk center). By this definition, we can find the magnetic pressure at the disk center,
\begin{equation}
p_{\mathrm{m_{\mathrm{c}}}} = p_{\mathrm{c}}/\beta_{\mathrm{c}}
\end{equation}
With the pressures at the center, we can also find the constants $K$ and $K_{\mathrm{m}}$ using the equations \eqref{eq:eos_fluid} and \eqref{eq:eos_mag}. And, for a given inner radius of the disk $r_{\mathrm{in}}$ we can find the potential $W_{\mathrm{in}}$. We now have all the elements required to find the enthalpy distribution (equation \eqref{eq:enthalpy_eq}), the pressure and magnetic pressure distribution (equations \eqref{eq:eos_fluid} and \eqref{eq:eos_mag}), and the density (equation \eqref{eq:density_eq}).

@@

As in \citet{Komissarov:2006}, in this paper we have chosen the exponents $\kappa = \eta = 4/3$ and the enthalpy at the disk center $w_{\mathrm{c}} = 0$. That leaves us the magnetization parameter $\beta_{\mathrm{c}}$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the black hole spin parameter $a$ and the inner radius of the disk $r_{\mathrm{in}}$. This allows us to control the size, shape, thickness and magnetization of the disk.

\begin{table}
\caption{List of models. Form left to right the columns report: the black hole spin $a$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the magnetization parameter $\beta_{\mathrm{c}}$ for which a maximum pressure is achieved, the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential diference between the center and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the disks, $r_{\mathrm{in}}$ and  $r_{\mathrm{out}}$. \tf{Complete table.}}             
\label{table:1}      
\centering          
\begin{tabular}{c c c c c c  c c c c}
\hline\hline       
 & $a$ & $\beta$ & $\gamma$ & $\beta_{\mathrm{c}}$  & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
\hline           
A1 & $0.5$ & $0.0$ & $0.0$ &  &  &    &  &  & \\ 
A2 &           & $0.5$ & $0.5$ &  &  &    &  &  & \\ 
A3  &          & $0.9$ & $0.9$ &  &  &    &  &  &  \\ 
A4  &          & $0.0$ & $0.9$ &  &  &    &  &  & \\ 
A5   &         & $0.9$ & $0.0$ &  &  &    &  &  & \\ 
A6   &         &           &           &  &  &    &  &  & \\ 
A7   &         &           &           &  &  &    &  &  &\\ 
 \hline 
B1 & $0.9$ & $0.0$ & $0.0$ &  &  &    &  &  & \\ 
B2 &           & $0.5$ & $0.5$ &  &  &    &  &  & \\ 
B3  &          & $0.9$ & $0.9$ &  &  &    &  &  &  \\ 
B4  &          & $0.0$ & $0.9$ &  &  &    &  &  & \\ 
B5   &         & $0.9$ & $0.0$ &  &  &    &  &  & \\ 
B6   &         &           &           &  &  &    &  &  & \\ 
B7   &         &           &           &  &  &    &  &  &\\  
 \hline 
C1 & $0.99$ & $0.0$ & $0.0$ &  &  &    &  &  & \\ 
C2 &             & $0.5$ & $0.5$ &  &  &    &  &  & \\ 
C3  &            & $0.9$ & $0.9$ &  &  &    &  &  &  \\ 
C4  &            & $0.0$ & $0.9$ &  &  &    &  &  & \\ 
C5   &           & $0.9$ & $0.0$ &  &  &    &  &  & \\ 
C6   &           &           &           &  &  &    &  &  & \\ 
C7   &           &           &           &  &  &    &  &  &\\   
\hline      
\end{tabular}
\end{table}

>>>>

\newcommand{\tf}[1]{\textcolor{red}{TF: #1}}
\newcommand{\sg}[1]{\textcolor{blue}{SG: #1}}

@@

   \author{Sergio Gimeno-Soler\inst{1}   \and Jos\'e A.~Font\inst{1,2} }

@@

   \keywords{accretion, accretion disks -- black hole physics -- magnetohydrodynamics (MHD)}

@@

Equilibrium tori around Kerr black holes are built assuming that the spacetime gravitational potentials and the fluid fields are stationary and axisymmetric. In all the derivations presented below, the Kerr metric is implicitely written using standard Boyer-Lindquist coordinates. It is convenient to introduce a number of relevant characteristic radii, such as the radius
of the marginally stable circular orbit, $r_{\rm ms}$, and the radius of the marginally bound circular orbit, $r_{\rm mb}$, given by
\begin{eqnarray}
r_{\rm ms} &=& M\,\left(3+Z_2-\left[(3-Z_1)(3+Z_1+2Z_2)\right]^{1/2})\right)\,,
\\
r_{\rm mb} &=& 2M\,\left(  1-\frac{a_*}{2} + \sqrt{1-a_*} \right)\,,
\end{eqnarray}
where we have defined the following quantities, $Z_1=1+(1-a_*^2)^{1/3}[(1+a_*)^{1/3}+(1-a_*)^{1/3}]$, $Z_2=(3a_*^2+Z_1^2)^{1/2}$, and $a_*=a/M$, with $a$ and $M$ being the spin Kerr parameter and the black hole mass.

@@

\cite{Jaroszynski:1980} argued that the slope of the specific angular momentum should range between two cases, $l = \mathrm{const.}$ and $\Omega = \mathrm{const}$. Following \citet{Qian:2009} we assume an angular momentum distribution ansatz given by  
\begin{equation}
l (r,\theta) = \left\{ \label{eq:ansatz} 
  \begin{array}{lr}
    l_0 \left(\frac{l_{\mathrm{K}}(r)}{l_0}\right)^{\beta}\sin^{2\gamma}{\theta} &  \text{for } r \geq r_{\mathrm{ms}}\\
    l_{\mathrm{ms}}(r)\sin^{2\gamma}{\theta} & \text{for } r < r_{\mathrm{ms}}
  \end{array}
\right.
\end{equation}
where constants $l_0$ and $l_{\mathrm{ms}}(r)$ are defined by $l_0 \equiv \eta l_{\mathrm{K}}(r_{\mathrm{ms}})$ and $l_{\mathrm{ms}}(r) \equiv l_0 [l_{\mathrm{K}}(r_{\mathrm{ms}})/l_0]^{\beta}$. Therefore, the model for the distribution of angular momentum has three parameters $(\beta, \gamma, \eta)$, whose range of variation is given by~\citep{Qian:2009}
\begin{equation}
0 \leq \beta \leq 1, \quad -1 \leq \gamma \leq 1, \quad 1 \leq \eta \leq \eta_{\mathrm{max}},
\end{equation}
with $\eta_{\mathrm{max}} = l_{\mathrm{K}}(r_{\mathrm{mb}})/l_{\mathrm{K}}(r_{\mathrm{ms}})$. In this paper, and as it is done in~\citet{Qian:2009}, we choose $\eta = \eta_{\mathrm{max}}$, and then we can write $l_0$ as $l_0 = l_{\mathrm{K}}(r_{\mathrm{mb}})$. For this choice of $\eta$, we can find the location of the disk cusp at $r_{\mathrm{mb}} \leq r_{\mathrm{cusp}} \leq r_{\mathrm{ms}}$ (for $0 \leq \beta \leq 1$). Also, this guarantees that constant angular momentum disks ($\beta = \gamma = 0$) with its inner edge located at the cusp ($r_{\mathrm{in}} = r_{\mathrm{cusp}}$) have no outer bound.

@@

The equations of ideal general relativistic MHD are the following conservation laws, $\nabla_{\mu} T^{\mu\nu} = 0$, $\nabla_{\mu} \,^\ast F^{\mu\nu} = 0$, and 
$\nabla_{\mu} (\rho u^{\mu}) = 0$, 
%\begin{equation}\label{eq:e-m_cons}
%\nabla_{\mu} T^{\mu\nu} = 0,
%\end{equation}
%\begin{equation}\label{eq:cons_faraday}
%\nabla_{\mu} \ast F^{\mu\nu} = 0,
%\end{equation}
%\begin{equation}\label{eq:continuity}
%\nabla_{\mu} (\rho u^{\mu}) = 0,
%\end{equation}
where $\nabla_{\mu}$ is the covariant derivative and
\begin{equation}\label{eq:e-m_tensor}
T^{\mu\nu} = (w + b^2)u^{\mu}u^{\nu} + \left(p + \frac{1}{2}b^2\right)g^{\mu\nu} - b^{\mu}b^{\nu},
\end{equation}
is the energy-momentum tensor of a magnetized perfect fluid, $w$ and $p$ being the fluid enthalpy and pressure, respectively. 
Moreover,
%\begin{equation}
$^\ast F^{\mu\nu} = b^{\mu}u^{\nu} - b^{\nu}u^{\mu}$
%\end{equation}
is the (dual of the) Faraday tensor relative to an observer with four-velocity $u^{\mu}$, and $b^{\mu}$ is the magnetic field in that frame, with
$b^2=b^{\mu}b_{\mu}$. Assuming the magnetic field is purely azimuthal, i.e.~$b^r = b^{\theta} = 0$,
and taking into account that the flow is stationary and axisymmetric, the conservation of the current density and of the Faraday tensor follow. Contracting Eq.~\eqref{eq:e-m_tensor} with the projection tensor $h^{\alpha}_{\beta} = \delta^{\alpha}_{\beta} + u^{\alpha}u_{\beta}$, we arrive at
\begin{equation}
(w + b^2)u_{\nu}\partial_i u^{\nu} + \partial_i\left(p + \frac{b^2}{2}\right) - b_{\nu}\partial_i b^{\nu}=0\,,
\end{equation}
where $i = r, \theta$. Following~\cite{Komissarov:2006} we rewrite this equation in terms of the specific angular momentum $l$ and the angular velocity $\Omega$, to obtain
\begin{equation}\label{eq:diff_ver}
\partial_i(\ln u_t|) - \frac{\Omega \partial_i l}{1-l\Omega} + \frac{\partial_i p}{w} + \frac{\partial_i(\mathcal{L}b^2)}{2\mathcal{L}w} = 0\,,
\end{equation}
where $\mathcal{L} = g_{t\phi}^2 - g_{tt}g_{\phi\phi}$.
To integrate Eq.~\eqref{eq:diff_ver} we first assume a barotropic equation of state $w = w(p)$ of the form
\begin{equation}\label{eq:eos_fluid}
p = K w^{\kappa},
\end{equation}
with $K$ and $\kappa$ constants.
Then, we define the magnetic pressure as $p_{\mathrm{m}} = b^2/2$, and introduce the definitions $\tilde{p}_{\mathrm{m}} = \mathcal{L} p_{\mathrm{m}}$ and $\tilde{w} = \mathcal{L} w$, in order to write an analog equation to Eq.~\eqref{eq:eos_fluid} for $\tilde{p}_{\mathrm{m}}$~\citep{Komissarov:2006}
\begin{equation}\label{eq:eos_mag_tilde}
\tilde{p}_{\mathrm{m}} = K_{\mathrm{m}} \tilde{w}_{\mathrm{m}}^{\lambda
},
\end{equation}
or, in terms of the magnetic pressure $p_{\mathrm{m}}$
\begin{equation}\label{eq:eos_mag}
p_{\mathrm{m}} = K_{\mathrm{m}} \mathcal{L}^{\lambda
-1} w^{\lambda
},
\end{equation}
where $K_{\mathrm{m}}$ and $\lambda
$ are constants.
This particular choice of relationships, $w = w(p)$ and $\tilde{w} = \tilde{w}(\tilde{p}_{\mathrm{m}})$, fulfill the general relativistic version of the von Zeipel theorem for a toroidal magnetic field~\citep{vonZeipel:1924, Zanotti:2015}, i.e.~the surfaces of constant $\Omega$ and constant $l$ coincide.

\begin{figure*}[t]
\centering
\includegraphics[scale=0.16]{figures/fig1a.pdf}
\hspace{-0.3cm}
\includegraphics[scale=0.16]{figures/fig1b.pdf}
\hspace{-0.2cm}
\includegraphics[scale=0.16]{figures/fig1c.pdf}
\caption{\sg{update figures.}Comparison with Komissarov's solution for a constant angular momentum model. The left panel shows the density distribution in logarithm scale for all radii and all angles while the middle and right panels show, respectively, the angular profile of the logarithm of the density at the centre of the disk and the radial profile of the density at the equatorial plane.}
           \label{komissarov}%
 \end{figure*}

Integrating Eq.~\eqref{eq:diff_ver} we obtain
\begin{equation}\label{eq:pre_full_int}
\ln |u_t| - \int^l_0 \frac{\Omega \mathrm{d}l}{1 - \Omega l} + \int^p_0 \frac{\mathrm{d}p}{w} + \int_0^{\tilde{p}_{\mathrm{m}}} \frac{\mathrm{d}\tilde{p}_{\mathrm{m}}}{\tilde{w}} = \mathrm{const}.
\end{equation}
On the surface of the disk, and particularly on its inner edge, the conditions
$p = \tilde{p}_{\mathrm{m}} = 0, \; u_t = u_{t, \mathrm{in}}, \; l = l_{\mathrm{in}}$
are satisfied and, therefore, the integration constant is simply given by
\begin{equation}
\mathrm{const.} = \ln |u_t| - \int^l_{l_\mathrm{in}} \frac{\Omega \mathrm{d}l}{1 - \Omega l}\,.
\end{equation}
We can also introduce the total (gravitational plus centrifugal) potential $W$~\citep{Abramowicz:1978} and write the integral form of the equation of motion as
\begin{equation}\label{eq:potential}
W - W_{\mathrm{in}} = \ln|u_t| - \ln|u_{t,\mathrm{in}}| - \int^{l}_{l_{\mathrm{in}}} \frac{\Omega \mathrm{d}l}{1 - \Omega l},
\end{equation}
where $W_{\mathrm{in}}$ is the potential at the inner edge of the disk (in the equatorial plane). With this definition, we can write Eq.~\eqref{eq:pre_full_int} as
\begin{equation}\label{eq:full_int}
W - W_{\mathrm{in}} = \int^p_0 \frac{\mathrm{d}p}{w} + \int_0^{\tilde{p}_{\mathrm{m}}} \frac{\mathrm{d}\tilde{p}_{\mathrm{m}}}{\tilde{w}},
\end{equation}
which for a barotropic equation of state can be easily integrated to give
\begin{equation}\label{eq:pre_enthalpy_eq}
W - W_{\rm{in}} + \frac{\kappa}{\kappa - 1}\frac{p}{w} + \frac{\lambda
}{\lambda
 - 1}\frac{p_{\mathrm{m}}}{w} = 0\,.
\end{equation}
Replacing $p$ and $p_{\mathrm{m}}$ by equations \eqref{eq:eos_fluid} and \eqref{eq:eos_mag}, the previous equation reduces to
\begin{equation}\label{eq:enthalpy_eq}
W - W_{\rm{in}} + \frac{\kappa}{\kappa - 1} K w^{\kappa - 1} + \frac{\lambda
}{\lambda
 - 1}K_{\mathrm{m}}(\mathcal{L} w)^{\lambda
 - 1} = 0,
\end{equation}
which relates the distribution of the potential with the distribution of enthalpy.

@@

@@

Next, we choose all the initial values for the integration of the equation \eqref{eq:F} to be between $r_{\mathrm{cusp}}$ and $r_{\mathrm{c}}$ ($\theta = \pi / 2$). Since we are only interested in the surfaces inside the Roche lobe, our choice of initial values provides us a mapping of the equipotential surfaces of the torus. Given that we have already obtained both the equipotential surfaces which cross the segment $[r_{\mathrm{cusp}}, r_{\mathrm{c}}]$ and the potential distribution there, we found the potential distribution for the torus.
Once we have the potential distribution, we can find the gas pressure at the center, from equation \eqref{eq:enthalpy_eq}
\begin{equation}
p_{\mathrm{c}} = w_{\mathrm{c}}(W_{\mathrm{in}} - W_{\mathrm{c}})\left(\frac{\kappa}{\kappa - 1} + \frac{\lambda
}{\lambda
 - 1}\frac{1}{\beta_{\mathrm{m}_{\mathrm{c}}}}\right)^{-1},
\end{equation}
where $w_{\mathrm{c}}$ is the enthalpy at the disk center and
\begin{equation}
\label{eq:beta_eq}
\beta_{\mathrm{m}} = p/p_{\mathrm{m}},
\end{equation}
is the magnetization parameter (being $\beta_{\mathrm{m}_{\mathrm{c}}}$ the magnetization parameter at the disk center). By this definition, we can find the magnetic pressure at the disk center,
\begin{equation}
p_{\mathrm{m_{\mathrm{c}}}} = p_{\mathrm{c}}/\beta_{\mathrm{m}_{\mathrm{c}}}
\end{equation}
With the pressures at the center, we can also find the constants $K$ and $K_{\mathrm{m}}$ using the equations \eqref{eq:eos_fluid} and \eqref{eq:eos_mag}. And, for a given inner radius of the disk $r_{\mathrm{in}}$ we can find the potential $W_{\mathrm{in}}$. We now have all the elements required to find the enthalpy distribution (equation \eqref{eq:enthalpy_eq}), the pressure and magnetic pressure distribution (equations \eqref{eq:eos_fluid} and \eqref{eq:eos_mag}), and the density (equation \eqref{eq:density_eq}).

@@

As in \citet{Komissarov:2006}, in this paper we have chosen the exponents $\kappa = \lambda
 = 4/3$ and the enthalpy at the disk center $w_{\mathrm{c}} = 1$. That leaves us the magnetization parameter $\beta_{\mathrm{m}_{\mathrm{c}}}
$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the black hole spin parameter $a$ and the inner radius of the disk $r_{\mathrm{in}}$. This allows us to control the size, shape, thickness and magnetization of the disk.

% \begin{table}
% \caption{List of models. Form left to right the columns report: the black hole spin $a$, the parameters of the angular momentum distribution $\beta$ and $\gamma$, the magnetization parameter $\beta_{\mathrm{m}_{\mathrm{c}}}
% $ at the disk center, the corresponding radii of the maximum thermal pressure and magnetic pressure, $r_{{\rm{max}}}$ and $r_{{\mathrm{m, max}}}$, the gravitational potential diference between the center and the inner radius, $\Delta W\equiv W_{\rm c}-W_{\rm in}$, and the inner and outer radii of the disks, $r_{\mathrm{in}}$ and  $r_{\mathrm{out}}$.}             
% \label{table:1}      
% \centering          
% \begin{tabular}{c c c c c c  c c c c}
% \hline\hline       
%  & $a$ & $\beta$ & $\gamma$ & $\beta_{\mathrm{m}_{\mathrm{c}}}
% $  & $r_{\rm{max}}$ &  $r_{\mathrm{m, max}}$ & $\Delta W$ & $r_{\mathrm{in}}$ & $r_{\mathrm{out}}$ \\ 
% \hline           
% A1 & $0.5$ & $0.0$ & $0.0$ & $10^{-3}$ &  $5.11$  & $5.51$ & $-6.35 \times 10^{-2}$ & $2.91$ & -- \\ 
% A2 &           & $0.5$ & $0.5$ &  & $5.55$ &  $5.80$  & $-2.27 \times 10^{-2}$ & $3.20$ & $11.77$\\ 
% A3  &          & $0.9$ & $0.9$ &  & $5.95$ &  $6.15$  & $-2.96 \times 10^{-3}$ & $3.70$ &  $9.583$\\ 
% A4  &          & $0.0$ & $0.9$ &  & $5.21$ &  $5.51$  & $-6.35 \times 10^{-2}$ & $2.91$ & $9.680$\\ 
% A5   &         & $0.9$ & $0.0$ &  & $5.90$ &  $6.10$  & $-2.95 \times 10^{-3}$ & $3.70$ & --\\ 
%  \hline 
% B1 & $0.9$ & $0.0$ & $0.0$ & $10^{-3}$ & $2.53$ &  $2.73$  & $-0.129$ & $1.73$ & -- \\ 
% B2 &           & $0.5$ & $0.5$ &  & $2.81$ &  $2.91$  & $-4.32 \times 10^{-2}$ & $1.86$ & $5.35$\\ 
% B3  &          & $0.9$ & $0.9$ &  & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & $4.52$\\ 
% B4  &          & $0.0$ & $0.9$ &  & $2.65$ &  $2.80$  & $-0.129$ & $1.732$ & $4.54$\\ 
% B5   &         & $0.9$ & $0.0$ &  & $3.03$ &  $3.13$  & $-5.39 \times 10^{-3}$ & $2.08$ & -- \\  
%  \hline 
% C1 & $0.99$ & $0.0$ & $0.0$ & $10^{-3}$ & $1.46$ & $1.51$ & $-0.246$ & $1.21$ & -- \\ 
% C2 &             & $0.5$ & $0.5$ &  & $1.56$ &  $1.61$  & $-7.34 \times 10^{-2}$ & $1.26$ & $2.50$\\ 
% C3  &            & $0.9$ & $0.9$ &  & $1.70$ &  $1.75$  & $-8.53 \times 10^{-3}$ & $1.35$ & $2.25$\\ 
% C4  &            & $0.0$ & $0.9$ &  & $1.50$ &  $1.57$  & $-0.246$ & $1.21$ & $2.26$\\ 
% C5   &           & $0.9$ & $0.0$ &  & $1.72$ &  $1.77$  & $-8.53 \times 10^{-3}$ & $1.35$ & --\\ 
% \hline      
% \end{tabular}
% \end{table}
